---
title: "2022Oct30_LearnToR_Introdplyr"
output: html_document
date: "2022-10-30"
---

#Objectives 

1.Learn how to download, install and activate packages in RStudio
2.Download available sample RNA-sequencing data from SeuratData package
3.Learn about dataframe (Data table)
4.Use dplyr package to select and filter dataframe 
5.Use table function to check the results of filtering 

# Download and Install package dplyr 

```{r}
print("Hello world! I am Quang")
```

```{r}
install.packages("dplyr")

library(dplyr)
```


# Download sample RNAseq data from Seurat package 

```{r}
install.packages("devtools")
library(devtools)

devtools::install_github('satijalab/seurat-data')

library(SeuratData)
SeuratData::InstallData("pbmc3k")
data("pbmc3k.final")

pbmc3k.final$groups <- sample(c("group1", "group2"), size = ncol(pbmc3k.final), replace = TRUE)

pbmc3k.final@meta.data -> dataFrame
  

```

# Inspect dataframe

```{r}
dataFrame

class(dataFrame)

dataFrame

View(dataFrame)
```

# dplyr functions: select, filter 

```{r}
dataFrame

colnames(dataFrame)

ncol(dataFrame)
nrow(dataFrame)

```


```{r}
#dplyr::select is a function in the dplyr package to select certain columns 
dataFrame %>% dplyr::select(seurat_clusters, groups) -> data2

# number rows x number columns 
data2[1:1000, ] -> data3
nrow(data2[1:1000, ])
```

```{r}
colnames(data2)

data2
```

```{r}
data3 %>% dplyr::filter(groups == "group1") %>% nrow()
```

```{r}
table(data3$groups)
```





